```{r echo=F}
library(ggplot2)
```
# MTCARS

You work for Motor Trend, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:


1. "Is an automatic or manual transmission better for MPG"
2. "Quantify the MPG difference between automatic and manual transmissions"

------------

### Executive Summary

Transmission is highly coorrelated but amount of cylinders plays a much more important role in the cars MPGs.
Manual cars have higher MPG on average but this is not always the case.

```{r fig.width=11, fig.height=11}
ggplot(mtcars, aes(x=am, y=mpg, fill=cyl)) + geom_boxplot() + facet_grid(. ~ cyl)
```


### Preparing the Dataset

To prepare the data, I transformed some variables into factors.

```{r}
data(mtcars)
mtcars$am <- factor(mtcars$am)
mtcars$cyl <- factor(mtcars$cyl)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
```

### Exploring the Dataset

Lets look at AM vs MPG.
```{r fig.width=11, fig.height=11}
ggplot(mtcars, aes(am, mpg)) + geom_boxplot() + scale_x_discrete(labels=c('Automatic', 'Manual'))
```
On average, a manual car (AM = 1) will have higher MPG. However we cannot conclude that automatic is better for MPG because we haven't looked at how the other variables interact.

Lets look at the other variables.
```{r fig.width=11, fig.height=11}
pairs(mtcars)
```
From this it is obvious that other variables such as cyl, disp, hp, wt, vs, gear and carb are also related to MPG.
We must study these interactions to reach a more robust conclusion.
### Fitting a Model

Lets use the noob canon and just try to fit a model with all the variables.
```{r fig.width=11, fig.height=11}
fit <- lm(mpg ~ . ,data=mtcars)
summary(fit)
```

From this it seems that cyl4 (intercept) is the most important.
Lets use R to find out the most important variables for this model.

```{r results='hide'}
new <- step(fit, direction='both')
```
```{r}
summary(new)
``` 
Now we know that the best model uses cyl + hp + wt + am.
First we want to know how accurate this is.
Lets look at the residuals

```{r fig.width=11, fig.height=11}
par(mfrow=c(2, 2))
plot(new_fit)
```


### Quantification

The model seems legit. Now lets look at this model to determine a few things.
```{r}
new_fit <- lm(formula = mpg ~ cyl + hp + wt + am - 1, data = mtcars)
summary(new_fit)
```

From this we can conclude that using manual instead of automatic increases your MPG by about 1.80.
However, the most important factor is cyl. Changing from 4 to 6 cylinders will reduce your MPG by about 3.
